Continuous Reinforcement Learning

### 2018-09-28 magnitudes.tex
Commit

Formally,
\begin{align}
	&V^\pi(s) - Q^\pi(s, a)\\ 
	= &\BE_{a'\sim \pi(\cdot\mid s)}
	\left[\tilde{r}(s, a') - \tilde{r}(s, a)\right] \deltat
	+
	\gamma^\deltat 
	(\BE\left[V^\pi(s_{t+\deltat}) \mid s_t=s\right]
	-
	\BE\left[V^\pi(s_{t+\deltat}) \mid s_t=s, a_t=a\right]).\nonumber
\end{align}
Now $s_{t + \deltat} = s_t + \F(s_t, a_t) \deltat +
\gauss(0, C(s_t, a_t)) \sqrt{\deltat}$, thus 
\begin{equation}
	V(s_{t+\deltat}) = V(s_t) + \partial_s V(s_t) \delta s_t
	+ \frac{1}{2}\mathrm{tr}(C(s_t, a_t) H_V(s_t))\deltat.
\end{equation}
In expectation, irrespective of wether the expectation is conditionned on $a$,
$V(s_{t+\deltat})$ and $V(s_t)$ are at distance $\bigO{\deltat}$. Consequently,
$V^\pi(s) - Q^\pi(s, a) = \bigO{\deltat}$.

@@

>>>>

Formally,
\begin{align}
	&V^\pi(s) - Q^\pi(s, a)\\ 
	= &\BE_{a'\sim \pi(\cdot\mid s)}
	\left[\tilde{r}(s, a') - \tilde{r}(s, a)\right] \deltat
	+
	\gamma^\deltat 
	(\BE\left[V^\pi(s_{t+\deltat}) \mid s_t=s\right]
	-
	\BE\left[V^\pi(s_{t+\deltat}) \mid s_t=s, a_t=a\right]).\nonumber
\end{align}
Now $s_{t + \deltat} = s_t + F(s_t, a_t) \deltat +
\gauss(0, C(s_t, a_t)) \sqrt{\deltat}$, thus 
\begin{equation}
	V(s_{t+\deltat}) = V(s_t) + \partial_s V(s_t) \delta s_t
	+ \frac{1}{2}\mathrm{tr}(C(s_t, a_t) H_V(s_t))\deltat.
\end{equation}
In expectation, irrespective of wether the expectation is conditionned on $a$,
$V(s_{t+\deltat})$ and $V(s_t)$ are at distance $\bigO{\deltat}$. Consequently,
$V^\pi(s) - Q^\pi(s, a) = \bigO{\deltat}$.

@@

\paragraph{An experimental validation of \tdz convergence.}
% {{{
As mentionned in the previous paragraph, the learning algorithms described
in~\ref{} are only expected to scale well if the value function approximated by
\tdz converges in some kind of $\ho$ norm, or at least a norm that involves
difference of function evaluations instead of function evaluations.

We evaluate the validity of this statement on a toy 2D problem, where the
value function can be efficiently nearly exactly approximated using finite
element methods. To simplify things, we work with fixed policy, and only
consider the state dynamic.

Consider a stochastic continuous dynamical system evolving as
\begin{equation}
	ds_t = (\omega J -\theta) (s_t - \mu) dt + \sigma dB_t
\end{equation}
where $s$ is a $2$-d vector, $J$ is $\begin{pmatrix} 0 & -1 \\ 1 & 0\end{pmatrix}$,
$\omega$ is an angular velocity parameter, $\mu$ is a mean parameter, $\theta$ is a
recall parameter and $\sigma$ is a noise parameter. A typical trajectory of this process
is given in Fig.~\ref{fig:trajectory}.
\begin{figure}
	\includegraphics[width=10cm]{imgs/trajectory.pdf}
	\caption{Example trajectory, $\mu=0$, $\sigma=0.3$, $\omega=0.5$,
	$\theta=0.03$}
	\label{fig:trajectory}
\end{figure}

Given a reward function $r\colon \statespace \to \R$, Bellman equation yields
\begin{equation}
	V(s_{t}) = \BE\left[\tilde{r}(s_t)dt\right] + (1 - (1 - \gamma)dt)\BE\left[V(s_{t+dt})\right]
\end{equation}
Using Ito's lemma,
\begin{align}
	V(s_{t}) &= \BE\left[\tilde{r}(s_t)dt\right] + (1 - (1 - \gamma)dt)\left(V(s_t) + \frac{\partial V}{\partial s}(s_t) (\omega J - \theta) (s_t - \mu) dt + \frac{\sigma^2}{2}\Delta V(s_t) dt\right)\nonumber\\
	(1 - \gamma) V(s_t) &= \BE\left[\tilde{r}(s_t)\right] + \frac{\partial V}{\partial s}(s_t) (\omega J - \theta) (s_t - \mu) + \frac{\sigma^2}{2}\Delta V(s_t).
\end{align}
This partial derivative equation is not directly solvable, but can be efficiently approximated
using finite element methods.

Important remarks:
\begin{itemize}
	\item Sampling i.i.d. from the trajectory seems to be extremely
		important. Estimating gradients using consecutive samples fails
		miserably (with NaNs early on, in setups where i.i.d. samples
		lead to convergence).
	\item Same goes for reward rescaling for high $\gamma$'s, an incorrect scaling
		will lead to quick divergence. TODO: test if computing mean on the fly
		suffices. TODO: Test if normalizing outputs suffices.
\end{itemize}
% }}}
